Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-12-03 Docs/IJES/journal.tex
minor changes

\maketitle

@@

Consequently, the second approach aims to remove the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}. This approach could potentially lead to great performance improvements, but as ESBMC checks for each step almost at the same rate, the processor does not remain idle for a longer period and thus there is almost no optimization.

@@

As an example, given a problem of domain from $1$ to $20$ (see Fig.~\ref{Binary-Step-Calculation}), we firstly create an initial interval from $1$ to $20$. When the next available core requests a step to be executed, the controller obtains the largest interval, {\it i.e.}, $\left[1,20\right]$, divides it by two, which creates two new intervals ({\it i.e.}, $\left[1,9\right]$ and $\left[11,20\right]$), and returns the middle of the original interval ({\it i.e.}, $10$). The controller also checks whether an interval has less than two elements to avoid creating empty or invalid intervals.

@@

Note that there might gaps between steps, which are produced by the customized binary-search. For instance, in the example shown in Fig.~\ref{Binary-Step-Calculation}, if step $10$ returns \textit{false}, then one can conclude that all steps after $10$ is \textit{false} as well. However, if the same step $10$ returns \textit{true}, we can assume that all steps before $10$ is \textit{true} as well. As a result, an auxiliary method to remove unnecessary steps is implemented in the controller by removing or shrinking existing intervals. This approach leads to a high impact in the verification time. However, if a step is running and is not needed anymore, the worker kills the forked process and starts a new one.

@@

\begin{lstlisting}[basicstyle=\footnotesize,caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=t,numberstyle=\tiny]
GetNextStep(){
 int largestChunk = -1;
 chunk largest;
 for each(chunk in chunks){
  if(chunk.right - chunk.left > largestChunk){
    largestChunk = chunk.right - chunk.left;
    largest = chunk;
  }
 }	
 chunks.remove(largest);	
 int median = largest.left + 
   floor((largest.right - largest.left) / 2);
 if(median > 0){
  if(largest.right - largest.left > 1)
   chunks.add(
     new chunk(largest.left, median - 1)
   );	
  if(largest.right != largest.left)
   chunks.add(
    new chunk(median + 1, largest.right)
   );
 }
 return median;
}
\end{lstlisting}

\vspace {2 mm}
Algorithm of Figure~\ref{worker-sample} describes how the worker starts and monitors ESBMC instances. The algorithm starts by retrieving the step to be executed from the controller (line $1$), then initiates the ESBMC instance and obtains the process \textit{id} from the forked process (line $2$). While the step is being executed, the controller checks whether this step is still needed (line $4$). If not, then the ESBMC instance is killed (line $5$) and the worker is free to initiate another step.

@@

%----------------------------------------------
\section{Experimental Evaluation}
\label{Experimental-Evaluation}
%----------------------------------------------

@@

%----------------------------------------------
\subsection{Description of Benchmarks}
\label{Benchmarks-Description}
%----------------------------------------------
To perform the experiments, some benchmarks provided by~\cite{Mann2007} were used, as shown in Table~\ref{tab:Description-of-Benchmarks}. The nodes in the graphs correspond to high-level language instructions. Software and communication costs are time dimensional, and hardware costs represent the occupied area. The first three benchmarks are extracted from MiBench, as shown in~\cite{Guthaus2001}. The clustering and fuzzy benchmarks are designed from~\cite{Mann2007} and are significantly large benchmarks. From the same authors, very complex benchmarks to test the limits of the applicability of techniques were used (RC$6$ and Mars).

\vspace{5 mm}
\hspace{-5 mm}
\begin{minipage}{\linewidth}
\centering
\small
\sffamily\small
\tabulinesep=4pt
\captionof{table}{Description of Benchmarks.} 
\begin{tabular}[c]{m{1.5cm}m{0.7cm}m{0.7cm}m{4.0 cm}}
\toprule[1.5pt]
\textbf{Name} & \textbf{Nodes} & \textbf{Edges} & \textbf{Description}\\
\midrule
\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check, as shown in~\cite{Guthaus2001}\\
\hline
\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily
\vspace{0.8 mm} Routine to insert values in Patricia Tree, as shown in ~\cite{Guthaus2001}\\
\hline
\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily \vspace{0.8 mm} Computer shortest paths in a graph, as shown in~\cite{Guthaus2001}\\
\hline
\verb|Clustering| & \verb|150| & \verb|331| & \rmfamily \vspace{0.8 mm} Image segmentation algorithm in a medical application\\
\hline
\verb|RC6| & \verb|329| & \verb|448| & \rmfamily \vspace{0.8 mm} RC6 cryptography graph algorithm\\
\hline
\verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily \vspace{0.8 mm} Clustering algorithm based on fuzzy logic\\
\hline
\verb|Mars| & \verb|417| & \verb|600| & \rmfamily 
\vspace{1 mm} MARS cipher from IBM algorithm\\
\bottomrule[1.5pt]
\label{tab:Description-of-Benchmarks} 
\end{tabular}\par
\bigskip
\end{minipage}

@@

%----------------------------------------------
\section{Conclusions}
\label{Conclusions}
%----------------------------------------------

>>>>

\maketitle
\clearpage

@@

\vspace{-5 mm}
Consequently, the second approach aims to remove the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}. This approach could potentially lead to great performance improvements, but as ESBMC checks for each step almost at the same rate, the processor does not remain idle for a longer period and thus there is almost no optimization.

@@

\vspace{-5 mm}
As an example, given a problem of domain from $1$ to $20$ (see Fig.~\ref{Binary-Step-Calculation}), we firstly create an initial interval from $1$ to $20$. When the next available core requests a step to be executed, the controller obtains the largest interval, {\it i.e.}, $\left[1,20\right]$, divides it by two, which creates two new intervals ({\it i.e.}, $\left[1,9\right]$ and $\left[11,20\right]$), and returns the middle of the original interval ({\it i.e.}, $10$). The controller also checks whether an interval has less than two elements to avoid creating empty or invalid intervals.

@@

\vspace{-4 mm}
Note that there might gaps between steps, which are produced by the customized binary-search. For instance, in the example shown in Fig.~\ref{Binary-Step-Calculation}, if step $10$ returns \textit{false}, then one can conclude that all steps after $10$ is \textit{false} as well. However, if the same step $10$ returns \textit{true}, we can assume that all steps before $10$ is \textit{true} as well. As a result, an auxiliary method to remove unnecessary steps is implemented in the controller by removing or shrinking existing intervals. This approach leads to a high impact in the verification time. However, if a step is running and is not needed anymore, the worker kills the forked process and starts a new one.

@@

\vspace{-1.5 mm}
\begin{lstlisting}[basicstyle=\footnotesize,caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=t,numberstyle=\tiny]
GetNextStep(){
 int largestChunk = -1;
 chunk largest;
 for each(chunk in chunks){
  if(chunk.right - chunk.left > largestChunk){
    largestChunk = chunk.right - chunk.left;
    largest = chunk;
  }
 }	
 chunks.remove(largest);	
 int median = largest.left + 
   floor((largest.right - largest.left) / 2);
 if(median > 0){
  if(largest.right - largest.left > 1)
   chunks.add(
     new chunk(largest.left, median - 1)
   );	
  if(largest.right != largest.left)
   chunks.add(
    new chunk(median + 1, largest.right)
   );
 }
 return median;
}
\end{lstlisting}

\vspace {-1.5 mm}
Algorithm of Figure~\ref{worker-sample} describes how the worker starts and monitors ESBMC instances. The algorithm starts by retrieving the step to be executed from the controller (line $1$), then initiates the ESBMC instance and obtains the process \textit{id} from the forked process (line $2$). While the step is being executed, the controller checks whether this step is still needed (line $4$). If not, then the ESBMC instance is killed (line $5$) and the worker is free to initiate another step.

@@

\vspace {-2 mm}
%----------------------------------------------
\section{Experimental Evaluation}
\label{Experimental-Evaluation}
%----------------------------------------------

@@

%----------------------------------------------
\subsection{Description of Benchmarks}
\label{Benchmarks-Description}
%----------------------------------------------

\begin{minipage}{\linewidth}
\centering
\small
\sffamily\small
\tabulinesep=4pt
\captionof{table}{Description of Benchmarks.} 
\begin{tabular}[c]{m{1.5cm}m{0.7cm}m{0.7cm}m{4.0 cm}}
\toprule[1.5pt]
\textbf{Name} & \textbf{Nodes} & \textbf{Edges} & \textbf{Description}\\
\midrule
\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check, as shown in~\cite{Guthaus2001}\\
\hline
\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily
\vspace{0.8 mm} Routine to insert values in Patricia Tree, as shown in ~\cite{Guthaus2001}\\
\hline
\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily \vspace{0.8 mm} Computer shortest paths in a graph, as shown in~\cite{Guthaus2001}\\
\hline
\verb|Clustering| & \verb|150| & \verb|331| & \rmfamily \vspace{0.8 mm} Image segmentation algorithm in a medical application\\
\hline
\verb|RC6| & \verb|329| & \verb|448| & \rmfamily \vspace{0.8 mm} RC6 cryptography graph algorithm\\
\hline
\verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily \vspace{0.8 mm} Clustering algorithm based on fuzzy logic\\
\hline
\verb|Mars| & \verb|417| & \verb|600| & \rmfamily 
\vspace{1 mm} MARS cipher from IBM algorithm\\
\bottomrule[1.5pt]
\label{tab:Description-of-Benchmarks} 
\end{tabular}\par
\bigskip
\end{minipage}

\vspace{-3 mm}
To perform the experiments, some benchmarks provided by~\cite{Mann2007} were used, as shown in Table~\ref{tab:Description-of-Benchmarks}. The nodes in the graphs correspond to high-level language instructions. Software and communication costs are time dimensional, and hardware costs represent the occupied area. The first three benchmarks are extracted from MiBench, as shown in~\cite{Guthaus2001}. The clustering and fuzzy benchmarks are designed from~\cite{Mann2007} and are significantly large benchmarks. From the same authors, very complex benchmarks to test the limits of the applicability of techniques were used (RC$6$ and Mars).

@@

\vspace {-4 mm}
%----------------------------------------------
\section{Conclusions}
\label{Conclusions}
%----------------------------------------------
